Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-01-21 Grassmannian_cells.tex
Random edits and notation changes

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Representation Theory of $K(n)$}\label{sec:RepK(n)}

@@

\subsection{Torus Actions}\label{torusaction}
Fix a vector space $X$ of dimension $n$ and let $k\leq n$.
We first consider a natural torus action on usual Grassmannians coming along with any direct sum decomposition of the vector space $X$.
Then we generalize the concept to quiver Grassmannians and observe that the torus fixed point sets can be calculated in an analogous manner.

Assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$.
We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of~$X$ which is compatible with this decomposition, i.e.\ there exist numbers $1\leq r_1\leq r_2\ldots\leq r_l\leq n$ such that
\[v_1,\ldots,v_{r_1}\in X_1,\quad v_{r_1+1},\ldots,v_{r_2}\in X_2,\quad\cdots\quad v_{r_l+1},\ldots,v_n\in X_l.\]
Moreover, we choose a map $d:\{1,\ldots,n\}\to\mathbb{Z}$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_{j}$ for some $j$.
Then there exists a $\C^\ast$-action on $X$ when linearly extending the definition $t.v_i:=t^{d(i)}v_i$ for $i=1,\ldots,n$ to all of~$X$.
This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_k(X)$.
We can represent each subspace~$U\in\Gr_k(X)$ uniquely as a matrix $M(U)$ in row-echelon form with respect to the basis $\mathcal B$, i.e.\ there exists a unique sequence $1\leq i_1\leq\ldots\leq i_k\leq n$ so that $M(U)$ is of the form
\[M(U):=\begin{pmatrix}\ast&\ldots &\ast &1&0 &\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&1&0&\ldots&\ldots&\ldots&\ldots&\ldots&0\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&0&\ast&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\vdots&\ddots&\ddots&\ddots&\ddots&\ddots&\vdots\\\ast&\ldots &\ast&0&\ast&\ldots &\ast&0&\ast&\ldots&\ast&1&0&\ldots&0\end{pmatrix}\in M_{k,n}(k),\]
where the unit vectors are in the columns $\bfi=(i_1,\ldots,i_k)$.
The set of all subspaces of $X$ represented by matrices of this fixed form define the \emph{Schubert cell} $X_\bfi$.
The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e.\ we have
\[(t.M(U))_{u,w}=t^{d(w)}\cdot M(U)_{u,w}\]
for $w=1,\ldots,n$.
Every Schubert cell is invariant under the torus action, i.e.\ $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
\begin{lemma}
  \label{usualGrass}
  Choose $d$ in such a way that $d(i)\neq d(i')$ if $v_i\in X_j$ and $v_{i'}\in X_{j'}$ with $j\neq j'$.
  Then we have $U\in X_{\bfi}^{\C^\ast}$ if and only if $U=\bigoplus_{i=1}^l U\cap X_i$.
\end{lemma}
\begin{proof}
  If $U=\bigoplus_{i=1}^l U\cap X_i$, we have 
\[t.U=\bigoplus_{i=1}^l t.(U\cap X_i)=\bigoplus_{i=1}^l t^{d(j_{i-1}+1)}(U\cap X_i)=U\]
where $j_0=0$.

Assume that $U$ is a torus fixed with $M(U)\in X_{\bfi}$. Fix the $w^{\mathrm{th}}$ column $M(U)_w$ and assume that $v_{w}\in X_s$. As the matrix representation $M(U)$ is uniquely determined, by the assumption on $d$, it follows that all matrix coefficients corresponding to a basis element $v_i$ such that $v_i\notin X_s$ are zero. This means that $\widehat{M(U)}_w\in X_s$ where $\widehat{M(U)}_w$ is the vector of $U$ corresponding to $M(U)_w$. As the colums are linear independent, this already shows the claim.
\end{proof}
The next step is to generalize this to quiver Grassmannians. Let $Q$ be an acyclic quiver. We choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\rep Q$ which can be lifted to $\hat Q$. We can consider the decomposition $X_q=\bigoplus_{(q,\chi)\in A_Q} X_{(q,\chi)}$. We define a torus action on each $X_{(q,\chi)}$ via $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ which can be extended linearly to each $X_q$. For a fixed a subspace $U_q$, we can define the subspace $t.U_q$. In general, this torus action induces no torus action on the quiver Grassmannians $\Gr_{\bfe}(X)$ as $t.U=(t.U_q)_{q\in Q_0}$ is no subrepresentation of $X$ for every $U\in \Gr_{\bfe}(X)$. Actually, such an action has to satisfy $X_{\alpha}(t.U_i)\in t.U_j$ for every $\alpha:i\to j$. 
\begin{lemma}Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
If $X\in\rep Q$ can be lifted, $d:\hat Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for all $\alpha:i\to j$ and $\chi\in A_{Q}$.
\end{lemma}
\begin{proof} 
  Let $U\in \Gr_\bfe(X)$. Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,\chi)}:X_{(i,\chi)}\to X_{(j,\chi+e_\alpha)}$. Let $u_{(i,\chi)}\in U_{(i,\chi)}$ and $\alpha:i\to j\in Q_1$. Then we have $X_\alpha(u_{(i,\chi)})\in U_{(j,\chi+e_\alpha)}$ because $X$ can be lifted to the universal cover. It follows
\[X_\alpha(t.u_{(i,\chi)})=X_\alpha(t^{d(i,\chi)}u_{(i,\chi)})=t^{d(i,\chi)}X_\alpha(u_{(i,\chi)})=t^{d(i,\chi)}u_{(j,\chi+e_\alpha)}=t^{-c_\alpha}t.u_{(j,\chi+e_\alpha)}\]
for some $u_{(j,\chi+e_\alpha)}\in U_{(j,\chi+e_\alpha)}$.
Now we have \[\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{c(j,\chi)}t.U_{(j,\chi)}\]
for every $t\in\C^\ast$ if $c(j,\chi)$ is constant along $(j,\chi)\in \{j\}\times A_Q$. This yields  
\[t.U_j=\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{-c_\alpha}t.U_{(j,\chi)}\]
for every $t\in \C^\ast$.
\end{proof}

\begin{lemma}
  \label{degreecondition} 
  Let $X$ be an indecomposable representation of $\hat Q$. There exists $d:\mathrm{supp} (X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that
	\begin{enumerate}
	\item for $(i,\chi),\,(j,\chi')\in\mathrm{supp}(X)$ with $(i,\chi)\neq (j,\chi')$ we have $d(i,\chi)\ne d(j,\chi')$;
	\item for $(i,\chi),\,(j,\chi')\in\mathrm{supp}(X)$, we have $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$.
	\end{enumerate}
\end{lemma}
\begin{proof}Assume that $|Q_1|=n$. Since $X$ is finite-dimensional and indecomposable, $\mathrm{supp}( X)$ is a connected and finite subquiver of $\hat Q$. In order to prove the statement, we may assume that $(q,0)\in \mathrm{supp}(X)$ for some $q\in Q_0$. We fix $c_\alpha\in\NN$ and show that we can choose a degree such that the two conditions are satisfied for this choice. Let $K$ be the maximal length of a path in $\mathrm{supp}(X)$ starting or ending in $(q,0)$ such that the underlying graph of the path has no cycles. This implies that, for $(q',\chi)\in\mathrm{supp}(X)$ with $\chi=\sum_{i=1}^nd_i\alpha_i$, we have $|d_i|\leq K$.

Set $c_{\alpha_1}=1$ and choose $c_{\alpha_j}$ recursively in such way that 
\[c_{\alpha_j}\geq 2(K+1)\sum_{i=1}^{j-1}c_{\alpha_i}\]
for $j=2,\ldots,n$.

Let $f:A_Q\to \ZZ$ be the group homomorphism defined by $f(\alpha)=c_\alpha$ for all $\alpha\in Q_1$ and define $d(q',\chi):=f(\chi)$ for $(q',\chi)\in\mathrm{supp}(X)$. In particular, for $(q',\chi)$ with $\chi=\sum_{i=1}^nd_i\alpha_i$, we have
\[d(q',\chi)=\sum_{i=1}^nd_ic_{\alpha_i}.\]

First note that we have $d(j,\chi+\alpha)-d(i,\chi)=c_\alpha$. Now assume that $d(i,\chi)=d(j,\chi')$ which means that $d(i,\chi)=\sum_{i=1}^{n}d_ic_{\alpha_i}=\sum_{i=1}^{n}e_ic_{\alpha_i}=d(j,\chi')$ if $\chi=\sum_{i=1}^{n}d_ic_{\alpha_i}$ and $\chi'=\sum_{i=1}^{n}e_ic_{\alpha_i}$. This implies
\[\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}=(e_{n}-d_{n})c_{\alpha_{n}}.\]
Since we have $|d_i-e_i|\leq 2K$ as $|d_i|,|e_i|\leq K$, we obtain $$|\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}|<2K\sum_{i=1}^{n-1}c_{\alpha_i}\leq c_{\alpha_n}$$
This inductively yields $d_i=e_i$ for $i=n,\ldots,1$ by the choice of $c_{\alpha_{i}}$.

Finally, assume that $d(j,\chi')-d(i,\chi)=c_\alpha$. Then we have $d(j,\chi')=d(j,\chi+e_\alpha)$. An analogous proof as the one above shows that $\chi'=\chi+e_\alpha$. Note that it is a priori possible that $(j,\chi+e_\alpha)\notin\mathrm{supp}(X)$. Thus we chose $c_{\alpha_j}$ in such a way that it is greater than $2(K+1)\sum_{i=1}^{j-1}c_{\alpha_i}$.

\end{proof}
In the following, we say that $d:\mathrm{supp}(X)\to\ZZ$ satisfies the degree condition for $X$ if it has the properties of Lemma \ref{degreecondition}.

\begin{theorem}Let $X$ be a representation which can be lifted to $\hat Q$ and choose $d:\mathrm{supp}(X)\to \ZZ$ such that it satisfies the degree condition for $X$. Then the torus action of $T$ on $\bigoplus_{q\in Q_0}X_q$ induced by $t.x_{(q,\chi)}=t^{d(q,\chi)}x_{(q,\chi)}$ for $x_{(q,\chi)}\in X_{(q,\chi)}$ induces
 a torus action on $\Gr_\bfe^Q(X)$ such that
  $$\Gr^Q_\bfe(X)^T\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X)$$ where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
\end{theorem}
\begin{proof}
A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U $ for all $t\in\C^\ast$, i.e. $t.U_q=U_q$ for all $q\in Q_0$, $t\in\C^\ast$. Thus, apart from being a subrepresentation of $X$, it is a fixed point of the torus actions on the usual Grassmannians $\Gr_{\bfe_q}(X_q)$ induced by the decompositions $X_q=\bigoplus_{\chi\in A_Q} X_{q,\chi}$. A subrepresentation $U\subset X$ can be lifted to the universal abelian covering if and only if
\[X_q\cap U_q=\bigoplus_{\chi\in A_Q} X_{(q,\chi)}\cap U_{(q,\chi)}=\bigoplus_{\chi\in A_Q}U_{(q,\chi)}.\]
Thus we can apply Lemma \ref{usualGrass} to obtain the claim.
\end{proof}
The next step is to iterate the torus action keeping in mind the following idea: every representation, which lifts to the universal covering quiver, also lifts to the universal abelian covering quiver and also to the iterated universal abelian covering quivers, i.e. to $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q=\hat Q^{(1)}$. Now it is straightforward to check that there exist natural surjective morphisms $f_k:\tilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}. Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 1$ such that the full subquiver with vertices $\mathrm{supp}(X)\subseteq \hat Q^{(k)}_0$ is a tree. Thus, if $\hat X^{(k)}$ is the lift of $X$ to $\hat Q^{(k)}$, there exists a torus action on the vector spaces $\hat X^{(k)}_q$ which induce a torus action on the quiver Grassmannian $\Gr_{\bfe}^{\hat Q^{(k)}}(\hat X^{(k)})$. If we denote the iterated torus fixed points by $\Gr^Q_\bfe(X)^{T^{(k)}}$. We obtain:
\begin{corollary}
Let $X$ be a representation which can be lifted to $\tilde Q$. Then there exists an iterated torus action such that
  $$\Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{\hat\bfe^{(k-1)}} \Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{\hat\bfe^{(k)}} \Gr^{\hat Q}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{\tilde\bfe} \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
\end{corollary}
%\begin{corollary}
%  affine bundles over $\Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $\Gr^Q_\bfe(X)$ is smooth
%  \[\{U\in \Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
%\end{corollary}
Define the $F$-polynomial of a representation $X$ by 
$$F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))x^\bfe\in\ZZ[x_i\mid i\in Q_0].$$

>>>>

\numberwithin{equation}{section}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Representation Theory of $K(n)$}
\label{sec:RepK(n)}

@@

\subsection{Torus Actions}
\label{torusaction}
Fix a vector space $X$ of dimension $n$ and let $k\leq n$.
We first consider a natural torus action on usual Grassmannians coming along with any direct sum decomposition of the vector space $X$.
Then we generalize the concept to quiver Grassmannians and observe that the torus fixed point sets can be calculated in an analogous manner.

Assume that $X=\bigoplus_{j=1}^l X_j$ is a direct sum decomposition of $X$.
We choose a basis $\mathcal B=\{v_1,\ldots,v_n\}$ of~$X$ which is compatible with this decomposition, i.e.\ there exist numbers $0=r_0<r_1<r_2<\cdots<r_{l-1}<r_l=n$ such that
\[v_{r_0+1},\ldots,v_{r_1}\in X_1,\quad v_{r_1+1},\ldots,v_{r_2}\in X_2,\quad\cdots\quad v_{r_{l-1}+1},\ldots,v_{r_l}\in X_l.\]
Moreover, we choose a map $d:\{1,\ldots,n\}\to\ZZ$ such that $d(i)=d(i')$ if $v_i,v_{i'}\in X_j$ for some $j$.
Then there exists a $\C^\ast$-action on $X$ when linearly extending the definition $t.v_i:=t^{d(i)}v_i$ for $i=1,\ldots,n$ to all of~$X$.
This naturally induces an action of $\C^\ast$ on the usual Grassmannians $\Gr_k(X)$.
We can represent each subspace~$U\in\Gr_k(X)$ uniquely as a matrix $M(U)$ in row-echelon form with respect to the basis $\mathcal B$, i.e.\ there exists a unique sequence $1\leq i_1<\ldots<i_k\leq n$ so that $M(U)$ is of the form
\[M(U):=
  \begin{pmatrix}
    \ast&\cdots &\ast &1&0 &\cdots& 0 & 0 & 0 &\cdots&0&0&0&\cdots&0\\
    \ast&\cdots &\ast&0&\ast&\cdots &\ast&1&0&\cdots&0&0&0&\cdots&0\\
    \ast &\cdots&\ast&0&\ast &\cdots&\ast&0&\ast&\cdots&0&0&0&\cdots&0\\[-0.4em]
    \vdots &\ddots&\vdots&\vdots&\vdots &\ddots&\vdots&\vdots&\vdots&\ddots&\vdots&\vdots&\vdots&\ddots&\vdots\\
    \ast&\cdots &\ast&0&\ast&\cdots &\ast&0&\ast&\cdots&0&0&0&\cdots&0\\
    \ast&\cdots &\ast&0&\ast&\cdots &\ast&0&\ast&\cdots&\ast&1&0&\cdots&0
  \end{pmatrix}\in M_{k,n}(k),\]
where the unit vectors are in the columns $\bfi=(i_1,\ldots,i_k)$.
The set of all subspaces of $X$ represented by matrices of this fixed form define the \emph{Schubert cell} $X_\bfi$.
The $\C^\ast$-action is then given by multiplying the $w^{\mathrm{th}}$ column with $t^{d(w)}$, i.e.\ we have
\[(t.M(U))_{u,w}=t^{d(w)}\cdot M(U)_{u,w}\]
for $w=1,\ldots,n$.
Every Schubert cell is invariant under the torus action, i.e.\ $t.M(U)\in X_\bfi$ for all $M(U)\in X_{\bfi}$. 
\begin{lemma}
  \label{usualGrass}
  Consider $d:\{1,\ldots,n\}\to\ZZ$ for which $d(i)\neq d(i')$ if $v_i\in X_j$ and $v_{i'}\in X_{j'}$ with $j\neq j'$.
  Then we have $U\in X_{\bfi}^{\C^\ast}$ if and only if $U=\bigoplus_{j=1}^l U\cap X_j$.
\end{lemma}
\begin{proof}
  If $U=\bigoplus_{j=1}^l U\cap X_j$, we have 
  \[t.U=\bigoplus_{j=1}^l t.(U\cap X_j)=\bigoplus_{j=1}^l t^{d(r_j)}(U\cap X_j)=U.\]
  Assume that $U$ is a torus fixed with $M(U)\in X_{\bfi}$.
  Fix the $w^{\mathrm{th}}$ column $M(U)_w$ and assume that $v_w\in X_j$. 
  As the matrix representation $M(U)$ is uniquely determined, the assumptions on $d$ imply that all matrix coefficients corresponding to a basis element $v_i$ with $v_i\notin X_j$ are zero.
  This means that $\widehat{M(U)}_w\in X_j$, where~$\widehat{M(U)}_w$ is the vector of $U$ corresponding to $M(U)_w$.
  As the colums are linearly independent, this already shows the claim.
The next step is to generalize this to quiver Grassmannians.
Let $Q$ be an acyclic quiver.
We choose a map $d:\hat Q_0\to\ZZ$ and fix a representation $X\in\rep Q$ which can be lifted to $\hat Q$.
We can consider the decomposition $X_i=\bigoplus_{(i,\chi)\in A_Q} X_{(i,\chi)}$.
We define a torus action on each $X_{(i,\chi)}$ via $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ which can be extended linearly to each $X_q$.
For a fixed a subspace $U_i$, we can define the subspace $t.U_i$.
In general, this torus action induces no torus action on the quiver Grassmannians $\Gr_\bfe(X)$ as $t.U=(t.U_i)_{i\in Q_0}$ is no subrepresentation of $X$ for every $U\in\Gr_\bfe(X)$.
Actually, such an action has to satisfy $X_\alpha(t.U_i)\in t.U_j$ for every $\alpha:i\to j$. 
\begin{lemma}
  Fix an integer $c_\alpha\in\ZZ$ for every $\alpha\in Q_1$.
  If $X\in\rep Q$ can be lifted, $d:\hat Q_0\to\ZZ$ induces a torus action on $\Gr_\bfe(X)$ if we have $d(j,\chi+e_\alpha)-d(i,\chi)=c_\alpha$ for all $\alpha:i\to j$ and $\chi\in A_Q$.
\end{lemma}
\begin{proof} 
  Let $U\in\Gr_\bfe(X)$. Since $X$ can be lifted, we can write $X_\alpha:X_i\to X_j$ as block matrix consisting of linear maps $X_{(\alpha,\chi)}:X_{(i,\chi)}\to X_{(j,\chi+e_\alpha)}$. Let $u_{(i,\chi)}\in U_{(i,\chi)}$ and $\alpha:i\to j\in Q_1$. Then we have $X_\alpha(u_{(i,\chi)})\in U_{(j,\chi+e_\alpha)}$ because $X$ can be lifted to the universal cover. It follows
\[X_\alpha(t.u_{(i,\chi)})=X_\alpha(t^{d(i,\chi)}u_{(i,\chi)})=t^{d(i,\chi)}X_\alpha(u_{(i,\chi)})=t^{d(i,\chi)}u_{(j,\chi+e_\alpha)}=t^{-c_\alpha}t.u_{(j,\chi+e_\alpha)}\]
for some $u_{(j,\chi+e_\alpha)}\in U_{(j,\chi+e_\alpha)}$.
Now we have \[\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{c(j,\chi)}t.U_{(j,\chi)}\]
for every $t\in\C^\ast$ if $c(j,\chi)$ is constant along $(j,\chi)\in \{j\}\times A_Q$. This yields  
\[t.U_j=\bigoplus_{\chi\in A_Q} t.U_{(j,\chi)}=\bigoplus_{\chi\in A_Q}t^{-c_\alpha}t.U_{(j,\chi)}\]
for every $t\in \C^\ast$.

\begin{lemma}
  \label{degreecondition} 
  Let $X$ be an indecomposable representation of $\hat Q$. There exists $d:\mathrm{supp} (X)\to\ZZ$ and $c_\alpha\in\mathbb N_+$ for each $\alpha\in Q_1$ such that
  \begin{enumerate}
    \item for $(i,\chi),\,(j,\chi')\in\mathrm{supp}(X)$ with $(i,\chi)\neq (j,\chi')$ we have $d(i,\chi)\ne d(j,\chi')$;
    \item for $(i,\chi),\,(j,\chi')\in\mathrm{supp}(X)$, we have $d(j,\chi')-d(i,\chi)=c_\alpha$ if and only if $\chi'=\chi+e_\alpha$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  Assume that $|Q_1|=n$.
  Since $X$ is finite-dimensional and indecomposable, the support quiver $\mathrm{supp}(X)$ is a connected and finite subquiver of $\hat Q$.
  In order to prove the statement, we may assume that $(i,0)\in\mathrm{supp}(X)$ for some $i\in Q_0$.
  We fix $c_\alpha\in\NN$ and show that we can choose a degree such that the two conditions are satisfied for this choice.
  Let $K$ be the maximal length of a path in $\mathrm{supp}(X)$ starting or ending in $(i,0)$ such that the underlying graph of the path has no cycles.
  This implies that, for $(i',\chi)\in\mathrm{supp}(X)$ with $\chi=\sum_{j=1}^n d_j\alpha_j$, we have $|d_j|\leq K$.

  Set $c_{\alpha_1}=1$ and choose $c_{\alpha_j}$ recursively in such way that 
  \[c_{\alpha_k}\geq 2(K+1)\sum_{j=1}^{k-1} c_{\alpha_j}\]
  for $k=2,\ldots,n$.

  Let $f:A_Q\to\ZZ$ be the group homomorphism defined by $f(\alpha)=c_\alpha$ for all $\alpha\in Q_1$ and define $d(i',\chi):=f(\chi)$ for $(i',\chi)\in\mathrm{supp}(X)$.
  In particular, for $(i',\chi)$ with $\chi=\sum_{j=1}^n d_j\alpha_j$, we have
  \[d(i',\chi)=\sum_{j=1}^n d_jc_{\alpha_j}.\]

  First note that we have $d(j,\chi+\alpha)-d(i,\chi)=c_\alpha$.
  Now assume that $d(i,\chi)=d(j,\chi')$ which means that $d(i,\chi)=\sum_{i=1}^n d_ic_{\alpha_i}=\sum_{i=1}^n e_ic_{\alpha_i}=d(j,\chi')$ if $\chi=\sum_{i=1}^n d_ic_{\alpha_i}$ and $\chi'=\sum_{i=1}^n e_ic_{\alpha_i}$.
  This implies
  \[\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}=(e_{n}-d_{n})c_{\alpha_{n}}.\]
  Since we have $|d_i-e_i|\leq 2K$ as $|d_i|,|e_i|\leq K$, we obtain 
  \[|\sum_{i=1}^{n-1}(d_i-e_i)c_{\alpha_i}|<2K\sum_{i=1}^{n-1}c_{\alpha_i}\leq c_{\alpha_n}.\]
  This inductively yields $d_i=e_i$ for $i=n,\ldots,1$ by the choice of $c_{\alpha_i}$.

  Finally, assume that $d(j,\chi')-d(i,\chi)=c_\alpha$.
  Then we have $d(j,\chi')=d(j,\chi+e_\alpha)$.
  An analogous proof as the one above shows that $\chi'=\chi+e_\alpha$.
  Note that it is a priori possible that $(j,\chi+e_\alpha)\notin\mathrm{supp}(X)$.
  Thus we chose $c_{\alpha_j}$ in such a way that it is greater than $2(K+1)\sum_{i=1}^{j-1}c_{\alpha_i}$. 
\end{proof}

In the following, we say that $d:\mathrm{supp}(X)\to\ZZ$ satisfies the \emph{degree condition} for $X$ if it has the properties of Lemma~\ref{degreecondition}.
\begin{theorem}
  Let $X$ be a representation which can be lifted to $\hat Q$ and choose $d:\mathrm{supp}(X)\to \ZZ$ such that it satisfies the degree condition for $X$.
  Then the torus action of $T$ on $\bigoplus_{i\in Q_0} X_i$ induced by $t.x_{(i,\chi)}=t^{d(i,\chi)}x_{(i,\chi)}$ for $x_{(i,\chi)}\in X_{(i,\chi)}$ induces a torus action on $\Gr_\bfe^Q(X)$ such that
  \[\Gr^Q_\bfe(X)^T\cong\bigsqcup_{\hat\bfe} \Gr^{\hat Q}_{\hat\bfe}(\hat X),\]
  where $\hat\bfe$ runs through all dimension vectors compatible with $\bfe$.
\end{theorem}
\begin{proof}
  A representation $U\in\Gr_{\bfe}(X)$ is a torus fixed point if and only if $t.U=U $ for all $t\in\C^\ast$, i.e.\ $t.U_i=U_i$ for all $i\in Q_0$, $t\in\C^\ast$.
  Thus, apart from being a subrepresentation of $X$, it is a fixed point of the torus actions on the usual Grassmannians $\Gr_{\bfe_i}(X_i)$ induced by the decompositions $X_i=\bigoplus_{\chi\in A_Q} X_{i,\chi}$.
  A subrepresentation $U\subset X$ can be lifted to the universal abelian covering if and only if
  \[X_i\cap U_i=\bigoplus_{\chi\in A_Q} X_{(i,\chi)}\cap U_{(i,\chi)}=\bigoplus_{\chi\in A_Q} U_{(i,\chi)}.\]
  Thus we can apply Lemma~\ref{usualGrass} to obtain the claim.
\end{proof}
The next step is to iterate the torus action keeping in mind the following idea: every representation, which lifts to the universal covering quiver, also lifts to the universal abelian covering quiver and also to the iterated universal abelian covering quivers, i.e. to $\hat Q^{(k)}:=\widehat{\hat Q^{(k-1)}}$ with $\hat Q=\hat Q^{(1)}$. Now it is straightforward to check that there exist natural surjective morphisms $f_k:\tilde Q\to \hat Q^{(k)}$ which become injective on finite subquivers if $k\gg 0$, see also \cite[Section 3.4]{wei}. Since the support of $X$ is finite as a representation of $\tilde Q$, we can find $k\geq 1$ such that the full subquiver with vertices $\mathrm{supp}(X)\subseteq \hat Q^{(k)}_0$ is a tree. Thus, if $\hat X^{(k)}$ is the lift of $X$ to $\hat Q^{(k)}$, there exists a torus action on the vector spaces $\hat X^{(k)}_q$ which induce a torus action on the quiver Grassmannian $\Gr_{\bfe}^{\hat Q^{(k)}}(\hat X^{(k)})$. If we denote the iterated torus fixed points by $\Gr^Q_\bfe(X)^{T^{(k)}}$. We obtain:
\begin{corollary}
Let $X$ be a representation which can be lifted to $\tilde Q$. Then there exists an iterated torus action such that
  $$\Gr^Q_\bfe(X)^{T^{(k)}}\cong \bigsqcup_{\hat\bfe^{(k-1)}} \Gr_{\hat\bfe^{(k-1)}}^{\hat Q^{(k-1)}}(\hat X^{(k-1)})^T\cong \bigsqcup_{\hat\bfe^{(k)}} \Gr^{\hat Q}_{\hat\bfe^{(k)}}(\hat X^{(k)})\cong \bigsqcup_{\tilde\bfe} \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$$ where $\hat\bfe^{(k-1)},\,\hat\bfe^{(k)},\,\tilde\bfe$ run through all dimension vectors compatible with $\bfe$.
\end{corollary}
%\begin{corollary}
%  affine bundles over $\Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)$ if $\Gr^Q_\bfe(X)$ is smooth
%  \[\{U\in \Gr^Q_\bfe(X):\lim_{t\to0} t\cdot U\in \Gr^{\tilde Q}_{\tilde\bfe}(\tilde X)\}\]
%\end{corollary}
Define the $F$-polynomial of a representation $X$ by 
$$F_X=\sum_{\bfe\in\NN^{Q_0}}\chi(\Gr_\bfe(X))x^\bfe\in\ZZ[x_i\mid i\in Q_0].$$
